Converting LaTeX Legacy R Journal Articles into R Markdown Articles using texor and rebib

### 2023-08-28 texor.Rmd
added a paragraph about alt-text

>>>>

One of the useful elements when an article is in HTML format is that figures can be made richer with an `alt-text` element. In an R Markdown code chunk generating a figure, this can be set using `fig.alt`. Alternative text provides a textual alternative to non-text content in HTML documents, serves various purposes: read by screen readers are accessible to people with visual disabilities, is displayed in place of the image if it fails to load, and can serve to assist search engines. It is a work in progress to have these added by authors of new article submissions, and at some potin would be useful to add to the converted legacy articles.

### 2023-08-28 texor.tex
added a paragraph about alt-text

>>>>

One of the useful elements when an article is in HTML format is that figures can be made richer with an \texttt{alt-text} element. In an R Markdown code chunk generating a figure, this can be set using \texttt{fig.alt}. Alternative text provides a textual alternative to non-text content in HTML documents, serves various purposes: read by screen readers are accessible to people with visual disabilities, is displayed in place of the image if it fails to load, and can serve to assist search engines. It is a work in progress to have these added by authors of new article submissions, and at some potin would be useful to add to the converted legacy articles.
